A Motion Capture and Imitation Learning-Based Approach to Robot Control

### 2022-06-19 tex-arxiv/article.tex
update abstract

\begin{abstract}
	Imitation Learning is a discipline of Machine Learning primarily concerned with replicating the behaviour of agents that are known to solve a particular task or family of tasks in a demonstration data set. In an industrial robotics context this presents the opportunity to replace explicit programming of behaviour with demonstrations of the task to be performed. Motion capture is one of the methods with which such demonstrations can be collected. It offers lesser model complexity compared to more indirect approaches such as ones based on visual data, yet requires additional data pre-processing if signals beyond effector position and orientation are relevant to the task at hand. In this paper, an approach for motion capture-based imitation learning and implicit control signal estimation is introduced and evaluated on an object throwing task.
\end{abstract}

>>>>

\begin{abstract}
	Imitation Learning is a discipline of Machine Learning primarily concerned with replicating the behaviour of agents that are known to solve a particular task or family of tasks in a demonstration data set. In an industrial robotics context this presents the opportunity to replace explicit programming of behaviour with demonstrations of the task to be performed. Motion capture is one of the methods with which such demonstrations can be collected. It offers lesser model complexity compared to more indirect observation modalities such as visual data, yet requires additional data pre-processing if signals beyond effector position and orientation are relevant to the task at hand. In this paper, an approach for motion capture-based imitation learning and implicit control signal estimation is introduced and evaluated on an object throwing task.
\end{abstract}
